The \dealii Library, Version 9.2

### 2020-05-14 9.2/paper.tex
Fix typos.
Remove a section no longer necessary.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Support for large, fully distributed meshes}
\label{subsec:pfT}

\todo[inline]{Peter: Write something about p::f::T}

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item The functions:
\begin{itemize}
\item \texttt{DoFHandler::loccaly\_owned\_dofs\_per\_processor()}
\item \texttt{DoFHandler::loccaly\_owned\_mg\_dofs\_per\_processor()}
\end{itemize} have been deprecated. As discussed in Subsection~\ref{subsec:performance}, deal.II does not store information for all processes on all processes processes, but only the local information or the locally-relevant information. Users are asked to construct the global information on their own, e.g. by calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item

>>>>

@@

The 9.2 release includes
\href{https://dealii.org/developer/doxygen/deal.II/changes_between_9_1_1_and_9_2_0.html}
     {around 60 incompatible changes}; see \cite{changes92}. The majority of these changes
should not be visible to typical user codes; some remove previously
deprecated classes and functions; and the majority change internal
interfaces that are not usually used in external
applications. However, some are worth mentioning:
\begin{itemize}
\item The functions:
\begin{itemize}
\item \texttt{DoFHandler::locally\_owned\_dofs\_per\_processor()}
\item \texttt{DoFHandler::locally\_owned\_mg\_dofs\_per\_processor()}
\end{itemize} have been deprecated. As discussed in Subsection~\ref{subsec:performance}, deal.II does not store information for all processes on all processes processes, but only the local information or the locally-relevant information. Users are asked to construct the global information on their own, e.g. by calling \texttt{Utilities::MPI::Allgather(locally\_owned\_info(), comm)}.
\item
